`phyr`: An R package for phylogenetic species-distribution modelling in ecological communities

### 2020-07-20 ms.Rmd
revision

In this example, the correlation between `trait1` and `trait2` is computed, and the column named `sp` in `data` identifies the species. The object `phy.sp` specifies the phylogenetic covariance matrix as a 'phylo' object from the `ape` package. `cor_phylo()` estimates the phylogenetic signal for each trait by assuming that trait evolution is given by a Ornstein-Uhlenbeck process. The term `covariates = list(trait1 ~ env)` includes the independent variable `env` for `trait1`, to remove possible confounding effects; only an intercept is estimated if no covariate is provided for a trait. Covariates are linear terms fit using ML or REML with the rest of the model. Within-species variation is specified by `meas_errors = list(trait1 ~ me1, trait2 ~ me2)`, where `me1` and `me2` are the standard errors for `trait1` and  `trait2`, respectively, of values at the tips of the phylogenetic tree. If within-species standard errors are not provided for a given trait, the trait values are assumed to be known without error. Finally, `cor_phylo()` can perform parametric bootstrapping to give confidence intervals for all parameter estimates: correlations, phylogenetic signals, covariate coefficients, and coefficient covariances.

@@

No data were used in this study. R code used to simulate data for PGLMMs as described in the Appendix is available at <https://github.com/daijiang/phyr_ms/blob/master/simulation_pglmm.R>. R code used to simulate data for comparative methods is available at <https://github.com/daijiang/phyr_ms/blob/master/simulation_cor_phylo.R>. `phyr` is available at Github (https://github.com/daijiang/phyr) and CRAN (https://cran.r-project.org/package=phyr).

@@

For demonstration purposes, we only simulated one functional trait and one environmental variable; in real datasets, multiple environmental variables and multiple functional traits can be included in the model.

>>>>

In this example, the correlation between `trait1` and `trait2` is computed, and the column named `sp` in `data` identifies the species. The object `phy.sp` specifies the phylogenetic covariance matrix as a 'phylo' object from the `ape` package. `cor_phylo()` estimates the phylogenetic signal for each trait by assuming that trait evolution is given by a Ornstein-Uhlenbeck process. The term `covariates = list(trait1 ~ env)` includes the independent variable `env` for `trait1`, to remove possible confounding effects; only an intercept is estimated if no covariate is provided for a trait. Covariates are linear terms fit using the generalized least squares estimation equation [@martins1997phylogenies]. Within-species variation is specified by `meas_errors = list(trait1 ~ me1, trait2 ~ me2)`, where `me1` and `me2` are the standard errors for `trait1` and  `trait2`, respectively, of values at the tips of the phylogenetic tree. If within-species standard errors are not provided for a given trait, the trait values are assumed to be known without error. Finally, `cor_phylo()` can perform parametric bootstrapping to give confidence intervals for all parameter estimates: correlations, phylogenetic signals, covariate coefficients, and coefficient covariances.

@@

No data were used in this study. R code used to simulate data for PGLMMs as described in the Appendix is available at <https://github.com/daijiang/phyr_ms/blob/master/simulation_pglmm.R>. R code used to simulate data for comparative methods is available at <https://github.com/daijiang/phyr_ms/blob/master/simulation_cor_phylo.R>. `phyr` is available at Github (https://github.com/daijiang/phyr) and CRAN (https://cran.r-project.org/package=phyr). Its documentations are available at <https://daijiang.github.io/phyr/index.html>.

@@

For demonstration purposes, we only simulated one functional trait and one environmental variable; in real datasets, multiple environmental variables and multiple functional traits can be included in the model. For examples using `pglmm()` to analyse empirical dataset, see the package vignette (<https://daijiang.github.io/phyr/articles/phyr_example_empirical.html>).
